The \dealii{} Library, Version 9.0

### 2018-04-10 9.0/paper.tex
fill-in Lapack/ScaLAPACK

\item
  Significant extension of matrix-free capabilities, including support for face integrals in discontinuous Galerkin schemes, a new Hermite-like polynomial basis adapted to face integrals that involve derivatives of shape functions, and several performance enhancements

@@

\item
  Increased support for dense solvers (LAPACK changes and new ScaLAPACK
  interface).

\item
  A dedicated sundials module has been created to provide support for the
  SUNDIALS library. SUNDIALS is a SUite of Nonlinear and
  DIfferential/ALgebraic equations Solvers. ARKode, IDA, and KINSOL are
  supported. ARKode is a solver library that provides adaptive-step time
  integration. IDA is a package for the solution of differential-algebraic
  equations systems in the form $F(t,y,y')=0$. KINSOL is olver for nonlinear
  algebraic systems.

>>>>

\item
  Significant extension of matrix-free capabilities, including support for face
  integrals in discontinuous Galerkin schemes, a new Hermite-like polynomial
  basis adapted to face integrals that involve derivatives of shape functions,
  and several performance enhancements.

@@

\item
  In this version we add template wrappers for ScaLAPACK -- parallel dense linear algebra
  library with block-cyclic matrix distribution over 2D process grid.
  The functionality and interface is similar to the LAPACK wrappers,
  matrix-matrix multiplication, Cholesky and LU factorizations,
  eigensolvers, SVD, pseudoinverse, save/load in HDF5 format and
  other functionality is implemented.
  A user can combine the new linear algebra with other MPI-parallel
  algorithms in \dealii{} without the need to worry about MPI communicator
  being divisible exactly into 2D process grid. The processes which are not part of
  the grid are labeled inactive and ScaLAPACK routines will not be called on them.
  %
  Additionally, we improved support of LAPACK. We added methods to perform
  rank-1 update/downdate, calculate Cholesky factorization, trace and determinant,
  as well as estimate the reciprocal condition number.
  We also now support configuration with 64-bit BLAS.

\item
  A dedicated sundials module has been created to provide support for the
  SUNDIALS library. SUNDIALS is a SUite of Nonlinear and
  DIfferential/ALgebraic equations Solvers. ARKode, IDA, and KINSOL are
  supported. ARKode is a solver library that provides adaptive-step time
  integration. IDA is a package for the solution of differential-algebraic
  equations systems in the form $F(t,y,y')=0$. KINSOL is solver for nonlinear
  algebraic systems.
